### 2021-09-09 README.Rmd
added example of conmat use to README for Sydney

```{r example}
library(conmat)
# build synthetic age-structured contact matrices with GAMs
# analysis of polymod data

>>>>

```{r get-syd}
library(conmat)
sydney_age_pop <- abs_age_lga("Sydney (C)")
sydney_age_pop
```

```{r sydney-synth-5, cache = TRUE}
synthetic_settings_5y_sydney <- extrapolate_polymod(
  population = sydney_age_pop,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)
synthetic_settings_5y_sydney
```

```{r sydney-synth-5-plot}
# this code is erroring for the moment - something to do with rendering a large plot I think.
# plot_setting_matrices(
#   synthetic_settings_5y_sydney,
#   title = "Setting-specific synthetic contact matrices (Sydney 2020 projected)"
# )
```

```{r plot-matrix-differents}
plot_matrix(synthetic_settings_5y_sydney$home)
plot_matrix(synthetic_settings_5y_sydney$work)
plot_matrix(synthetic_settings_5y_sydney$school)
plot_matrix(synthetic_settings_5y_sydney$other)
plot_matrix(synthetic_settings_5y_sydney$all)
```

```{r example}
# build synthetic age-structured contact matrices with GAMs
# analysis of polymod data
